---
title: "Contact Gap Analysis"
author: "Jesse Cahill"
date: "September 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(lubridate)
```

# Read and Tidy Address Data

```{r warning=FALSE, message=FALSE}
add <- read_csv(str_c("C:\\Users\\jc4673\\Documents\\Columbia\\CHS_Lexis\\distance_measures\\",
"chs_lexisnexis_distance_measures_2\\chs_addresses_geocode__chs_addresses_geocode.csv"), 
                col_types = cols_only(ssn_altkey = "c",
                                     yrdeath = "i",
                                     dxid1 = "i",
                                     dxid2 = "i",
                                     chs_entrydate1 = col_date(),
                                     chs_entrydate2 = col_date()
                                     ))
#add


# Separate table for year of death
yrdeath <- add %>%
    select(ssn_altkey, yrdeath) %>%
    distinct()

# Separate tables for id1 & id2, to be joined later on
id1 <- add %>%
    select(ssn_altkey, dxid1, chs_entrydate1) %>%
    distinct() %>%
    rename(id = dxid1, chs_entrydate = chs_entrydate1)

id2 <- add %>%
    select(ssn_altkey, dxid2, chs_entrydate2) %>%
    distinct() %>%
    rename(id = dxid2, chs_entrydate = chs_entrydate2)

# Tidy version of address start dates
tidy_entry <- bind_rows(id1, id2) %>%
    distinct() %>%
    select(-id) %>%
    group_by(ssn_altkey) %>%
    mutate(id = row_number()) %>%
    arrange(ssn_altkey, id) %>%
    select(ssn_altkey, id, chs_entrydate)

#tidy_entry
```

# Contact Date Data

```{r}
contact_date <- read_dta("C:\\Users\\jc4673\\Documents\\Data\\CHS\\contactsbyalt_keywdates.dta") %>%
    group_by(ssn_altkey) %>%
    mutate(next_date = lead(contactdate),
          gap = next_date - contactdate) %>%
    ungroup %>% 
    na.omit #%>%
    #mutate(gap_interval = interval(contactdate, next_date))

#contact_date

#interval(contact_date$contactdate, contact_date$next_date)
```
 
```{r}
g <- ggplot(contact_date, mapping = aes(x = gap))
 g + geom_histogram(bins = 100)
 g + geom_density(color = "Blue")
```

## Conclusions (Gap Distributions):
The data is bi-modal, with a large peak appearing at 6 months and a much smaller one appearing at 1 year. Of **`r nrow(contact_date)`** contacts, **`r nrow(filter(contact_date, gap > days(365)))`** have intervals longer than one year.

# Address Change After Gap?

First, we subset the data to only gaps greater than 1 year.

```{r}

g_1yr <-contact_date %>% 
  #select(-gap_interval) %>% 
  filter(gap > 365) %>%
  select(ssn_altkey, contactdate, everything()) %>% 
  arrange(ssn_altkey, contactdate) 
```  

Now, we join the gap data with the chs new address data, and filter for when a new address appears within a gap. 

```{r}
joined <- inner_join(g_1yr, tidy_entry) %>% 
  mutate(gap_interval = interval(contactdate, next_date))
joined_filter <- with(joined, joined[chs_entrydate %within% gap_interval, ])

#joined_filter

```

All in all, this leads to **`r nrow(joined_filter)`** gaps of over 365 days that contained an address change, out of **`r nrow(g_1yr)`** total gaps >= 365 days. These gaps can be attributed to **`r nrow(distinct(joined_filter, ssn_altkey))`** unique patients.




